A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/prab.tex

A modular multi-objective software framework was developed (see
  Fig.~\ref{fig:framenetwork}) where the core functionality is decoupled from
  the ``forward solver'' and the optimizer.
To that end, we use a master/slave mechanism where a master process governs a
  set of slave processes given some computational tasks to complete.
This separation allows easy interchange of optimization algorithms, forward
  solvers and optimization problems.
A ``pilot'' coordinates all efforts between the optimization algorithm and the
  forward solver.
This forms a robust and general framework for massively parallel
  multi-objective optimization.
Currently the framework offers one concrete optimization algorithm, an
  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
Normally, simulation based approaches are plagued by the trade-of between
  level of detail and time to solution.
We address this problem by using forward solvers with different time and
  resolution complexity.

@@

In most cases \textsc{Simulation} implementations are simple wrappers to run
  an existing ``external'' simulation code using a set of design variables as
  input.
As for the \textsc{Optimizer} component there exists a base class, labeled
  \texttt{Simulation} as common basis for all \textsc{Simulation}
  implementations.
In addition, this component also inherits from the \texttt{Worker} class,
  already implementing the polling protocol for default worker types.
As shown in the API in Listing 3, the \texttt{Worker} class expects an
  implementation to provide implementations for those three methods.

>>>>

A modular multi-objective software framework was developed (see
 Fig.~\ref{fig:framenetwork}) where the core functionality of the optimizer is decoupled from
 the ``beam dynamics'' but fully integrated in the OPAL \cite{opal} framework. 
To that end, we use a master/slave mechanism where a master process governs a
 set of slave processes given some computational tasks (beam dynamics simulation) to complete.
This separation allows easy interchange of optimization algorithms, forward
  solvers and optimization problems.
A ``pilot'' coordinates all efforts between the optimization algorithm and the
  beam dynamics task. In the sequel we will also use the notion of ``forward solver'' to indicate 
  the beam dynamics task.
This forms a robust and general framework for massively parallel
  multi-objective optimization.
Currently the framework offers one concrete optimization algorithm, an
  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
Normally, simulation based approaches are plagued by the trade-of between
  level of detail and time to solution.
We address this problem later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
  resolution complexity.

@@

In most cases forward solver implementations are simple wrappers to run
  an existing ``external'' simulation code using a set of design variables as
  input. In case of the OPAL integration, basically the \texttt{main} function is
  playing the role of the ``forward solver''. Underlying the general nature of our approach, 
  in a similar project, we use the described methods for cavity shape optimisation based on \cite{ARBENZ2008381}. 
As for the \textsc{Optimizer} component there exists a base class, labeled
  \texttt{Simulation} as common basis for all \textsc{Simulation}
  implementations.
In addition, this component also inherits from the \texttt{Worker} class,
  already implementing the polling protocol for default worker types.
As shown in the API in Listing 3, the \texttt{Worker} class expects an
  implementation to provide implementations for those three methods.
